### 2017-03-03 Lab_4/solutions/L4-1-2.tex
Writing Lab_4 report, finished up to and including WEP. Also limited the large tcpdump file as requested in the assignment.
Changed some previous L4 answers, added L4-5 anwers with new trace file, cleaned up L4 traces

The SSID itself can still be seen in following packet / frame types, despite SSID hiding:
\begin{itemize}
\item PacketID 455  , Probe Request
\item PacketID 456  , Probe Response
\item PacketID 617  , Association Request
\end{itemize}
The beacon frames sent by our AP can no longer be used to determine the SSID but other traffic still works.
With the parameter being "ignore_broadcast_ssid", it was to be expected only the beacon frames would no longer contain the SSID.

>>>>

The SSID itself can still be seen in following packet / frame types, despite SSID hiding:
\begin{itemize}
\item Probe Request (packet 455)
\item Probe Response (packet 456)
\item Association Request (packet 617)
\end{itemize}
The SSID was only removed from the broadcast beacon frames, the others are unchanged. Note that the beacon frames are still sent. In Wireshark's packet info field the SSID is shown as "Broadcast" but further inspection of the packet shows the SSID field is simply empty.
With the parameter being "ignore\_broadcast\_ssid", it was to be expected only the beacon frames would no longer contain the SSID.

### 2017-03-03 Lab_4/solutions/L4-4-1.tex
Changed some previous L4 answers, added L4-5 anwers with new trace file, cleaned up L4 traces

Difference : WEP parameters 4 bytes + 4 bytes that dont show up when you look at wep params in the pkt
IV en key index voor data, WEP ICV na data maar voor fcs

>>>>

The difference in size between the encrypted packet with ID 1415 in traces/L4-3-1.STA2.wep.pcap and the regular (non-WEP) packet with ID 1077 in traces/L4-3-1.STA2.pcap is 8 bytes (154 vs 146).
The extra 8 bytes are the WEP parameters in the IEEE 802.11 Data header. These WEP parameters are an initialization vector (3 bytes), a key index (1 byte) and a WEP Integrity Check Value (4 bytes). This ICV is inserted between the encrypted data and the frame check sequence.
